experiment 1

### 2021-11-12 experiments/experiment 1/experiment-1.Rmd
with testing of new version

# default_dynamic_model <- bushplus_dynamic_model
# default_event_definition <- event_definition_1
# default_event_interval <- 100
# default_noise_sigma <- 0
# default_minimum_abundances <- rep(1, 3)
# names(default_minimum_abundances) <- c("CB", "PB", "SB")
# default_sim_duration <- 80000
# default_sim_sample_interval <- 100
# initial_pars_from <- "bush_ssfig3"
## note that next line (log10a_series is over-ridden with getting stable states)
#default_log10a_series <- c(-2, -2, -2, -2, -10, -10, -10, -10, -10)

@@

sp <- new_strain_parameter(
  n_CB = 9,
  n_PB = 9,
  n_SB = 9,

  values_initial_state = "bush_ssfig3"
)

@@

## num_div_treatment_levels <- 3 ## FOR TEST

@@

```{r}
var_expt_levels <- var_expt[, 1:6]

@@

max_only_SBPB_diversity <- which(
  max(rowSums(abs(var_expt_levels[, 3:6]))) == rowSums(abs(var_expt_levels[, 3:6])) &
  rowSums(abs(var_expt_levels[, 1:2])) == 0
)
#var_expt_levels[20,]
```

@@

```{r eval = eval_dynamics_flag}
# default_sim_duration <- 80000
parameter$sim_duration <- 80000
```

```{r eval = eval_dynamics_flag}
# default_log10a_series <- c(-1, -7, -7)
parameter$log10a_series <- c(-1, -7, -7)
parameter$strain_parameter <- var_expt$pars[[no_diversity]]
parameter$strain_parameter$initial_state <- new_initial_state(
  num_CB_strains,
  num_PB_strains,
  num_SB_strains,
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/num_CB_strains
sim_res_novar1 <- run_simulation(parameter)
saveRDS(sim_res_novar1, here("experiments/experiment 1/data/sim_res_novar1.RDS"))
```

@@

```{r eval = eval_dynamics_flag}
# Is this actually needed?
# sim_number <- num_div_treatment_levels
try_me <- 311
#sim_number2 <- num_div_treatment_levels
parameter$strain_parameter <- var_expt$pars[[try_me]]
#parameter$strain_parameter <- var_expt$pars[[max_diversty_all]]
parameter$strain_parameter$initial_state <- sim_res_novar1$strain_parameter$initial_state
sim_res_highvar1 <- run_simulation(parameter)
saveRDS(sim_res_highvar1, here("experiments/experiment 1/data/sim_res_highvar1.RDS"))
```

@@

```{r eval = eval_dynamics_flag}
# sim_number <- 1
parameter$log10a_series <- c(-5, -3, -1, -1)
parameter$strain_parameter <- var_expt$pars[[no_diversity]]
parameter$strain_parameter$initial_state <- new_initial_state(
  num_CB_strains,
  num_PB_strains,
  num_SB_strains,
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
sim_res_novar2 <- run_simulation(parameter)
saveRDS(sim_res_novar2, here("experiments/experiment 1/data/sim_res_novar2.RDS"))
```

@@

```{r eval = eval_dynamics_flag}
#sim_number <- num_div_treatment_levels
try_me <- 311
#sim_number2 <- num_div_treatment_levels
parameter$strain_parameter <- var_expt$pars[[try_me]]
#parameter$strain_parameter <- var_expt$pars[[max_diversty_all]]
parameter$strain_parameter$initial_state <- sim_res_novar2$strain_parameter$initial_state
sim_res_highvar2 <- run_simulation(parameter)
saveRDS(sim_res_highvar2, here("experiments/experiment 1/data/sim_res_highvar2.RDS"))
```

@@

```{r eval = eval_dynamics_flag}
# sim_number1 <- 1
parameter$log10a_series <- c(-1, -8, -1)
parameter$strain_parameter <- var_expt$pars[[no_diversity]]
parameter$strain_parameter$initial_state <- new_initial_state(
  num_CB_strains,
  num_PB_strains,
  num_SB_strains,
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
sim_res_novar3 <- run_simulation(parameter)
saveRDS(sim_res_novar3, here("experiments/experiment 1/data/sim_res_novar3.RDS"))
```

@@

```{r eval = eval_dynamics_flag}
try_me <- 311
#sim_number2 <- num_div_treatment_levels
parameter$strain_parameter <- var_expt$pars[[try_me]]
parameter$strain_parameter$initial_state <- sim_res_novar3$strain_parameter$initial_state
sim_res_highvar3 <- run_simulation(parameter)
saveRDS(sim_res_highvar3, here("experiments/experiment 1/data/sim_res_highvar3.RDS"))
```

@@

### Visualise

@@

```{r}
# default_sim_duration <- 1000000
# ssfind_minimum_abundances <- rep(0, 3)
# names(ssfind_minimum_abundances) <- c("CB", "PB", "SB")
# sfind_simulation_duration <- default_sim_duration
# ssfind_simulation_sampling_interval <- ssfind_simulation_duration
# ssfind_event_interval <- ssfind_simulation_duration

minimum_abundances <- rep(0, 3)
names(minimum_abundances) <- c("CB", "PB", "SB")

## grid_num_a <- 1000 #usually 1000 ## number of a_0 values
grid_num_a <- 100 ## FOR TEST

a_Os <- 10^seq(-7, -0.5, length=grid_num_a) ## sequence of a_0 values
grid_num_N <- 2 ## number of N values
initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
initial_PBs <- 1e8 ## not varied
initial_SBs <- 1e8 ## not varied
# next line creates all possible combinations
ss_expt <- expand.grid(N_CB = initial_CBs,
                      N_PB = initial_PBs,
                      N_SB = initial_SBs,
                      a_O = a_Os)

parameter <- new_ss_by_a_N_parameter(
  dynamic_model = parameter$dynamic_model,
  event_definition = parameter$event_definition,
  event_interval = 1000000,
  noise_sigma = parameter$noise_sigma,
  minimum_abundances = minimum_abundances,
  sim_duration = 1000000,
  sim_sample_interval = 1000000,
  log10a_series = parameter$log10a_series,
  solver_method = parameter$solver_method,
  ss_expt = ss_expt
)
rm(minimum_abundances, grid_num_a, a_Os, grid_num_N, initial_CBs, initial_PBs, initial_SBs, ss_expt)
saveRDS(parameter, here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS"))
saveRDS(var_expt, here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial.RDS"))
```

@@

## sim length 80'000, 20 x 20 factorial, reference maximum diversity
# readRDS(here("experiments/experiment 1/data/ss_data_80000.RDS")) %>%
#   mutate(sim_length = 80000) %>% 
#   multidplyr::partition(cluster) %>%
#   mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
#   collect() %>%
#   unnest(cols = c(stability_measures)) %>%
#   saveRDS(here("experiments/experiment 1/data/stab_data_80000.RDS"))

## sim length 1'000'000, 20 x 20 factorial, reference maximum diversity
# readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS")) %>%
#   mutate(sim_length = 1000000) %>% 
#   multidplyr::partition(cluster) %>%
#   mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
#   collect() %>%
#   unnest(cols = c(stability_measures)) %>%
#   saveRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))

## sim length 1'000'000, 20 SBPBgrad, 5x maximum diversity
# readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS")) %>%
#   mutate(sim_length = 1000000) %>% 
#   multidplyr::partition(cluster) %>%
#   mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
#   collect() %>%
#   unnest(cols = c(stability_measures)) %>%
#   saveRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))

## sim length 300'000, 20 SBPBgrad, reference maximum diversity
# readRDS(here("experiments/experiment 1/data/ss_data_300000_small.RDS")) %>%
#   mutate(sim_length = 300000) %>% 
#   multidplyr::partition(cluster) %>%
#   mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
#   collect() %>%
#   unnest(cols = c(stability_measures)) %>%
#   saveRDS(here("experiments/experiment 1/data/stab_data_300000.RDS"))

## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS")) %>%
  mutate(sim_length = 1000000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
```

## SS, no diversity, all diversity, CB only, and SBPB only
No Experimental data

```{r, eval = FALSE, echo = FALSE}
## find various combinations of diversity
var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS"))

```{r, eval = FALSE, echo = FALSE}

```{r, eval = FALSE, echo = FALSE}

```{r, eval = FALSE, echo = FALSE}

```{r, eval = FALSE, echo = FALSE}

```{r, eval = FALSE, echo = FALSE}
p_overlay1 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
                             var_expt[max_diversty_all,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay1
```

```{r, eval = FALSE, echo = FALSE}
p_overlay2 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
                             var_expt[max_only_CB_diversity,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay2

```{r, eval = FALSE, echo = FALSE}
p_overlay3 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
                             var_expt[max_only_SBPB_diversity,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay3

## Look at stability measures
No experimental data.

### Calculations
```{r, eval = FALSE, echo = FALSE}
stab_data <- bind_rows(
  readRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS")), 
  readRDS(here("experiments/experiment 1/data/stab_data_80000.RDS"))
)

CB_vars <- unique(stab_data$CB_var_gmax_s)
SB_vars <- unique(stab_data$CB_var_gmax_s)

saveRDS(all_stab_results, here("experiments/experiment 1/data/all_stab.RDS"))
```

### Plot raw
```{r, eval = FALSE, echo = FALSE}

all_stab_results <- readRDS(here("experiments/experiment summary/all_stab.RDS"))

all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range_raw, col=var_treat, shape = as_factor(sim_length))) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O",
         sim_length == 8e4) %>%
  ggplot(aes(x = var_gmax,
             ymin = hyst_min_raw,
             ymax = hyst_max_raw,
             fill=var_treat)) +
  geom_ribbon(alpha = 0.5) +
  facet_wrap( ~ var_treat, nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

bind_rows(
  readRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS")), 
  readRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
) %>%
  filter(
    Species == "O",
    sim_length == 1e6
  ) %>%
  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_raw, col = hyst_range_raw)) +
  geom_point(size = 3)

### Plot log
```{r, eval = FALSE, echo = FALSE}

all_stab_results <- readRDS(here("experiments/experiment summary/all_stab.RDS"))

all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range_log, col=var_treat, shape = as_factor(sim_length))) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O",
         sim_length == 8e4) %>%
  ggplot(aes(x = var_gmax,
             ymin = hyst_min_log,
             ymax = hyst_max_log,
             fill=var_treat)) +
  geom_ribbon(alpha = 0.5) +
  facet_wrap( ~ var_treat, nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

bind_rows(
  readRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS")), 
  readRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
) %>%
  filter(
    Species == "O",
    sim_length == 1e6
  ) %>%
  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_log, col = hyst_range_log)) +
  geom_point(size = 3)

## Extra SBPB diversity
No experimental data.

```{r, eval = FALSE, echo = FALSE}
var_expt_x <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS"))
stab_data_x <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))

p1  <- plot_ss_result1(var_expt_x,
                result_index = 1,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1

p1  <- plot_ss_result1(var_expt_x,
                result_index = 19,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1

p_overlay1 <- plot_ss_result2(var_expt_x[1,]$ss_res[[1]],
                             var_expt_x[19,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay1
```

### raw
```{r, eval = FALSE, echo = FALSE}
stab_data_x %>%
  filter(Species == "O") %>%
  ggplot(aes(x = SB_var_gmax_s, y = hyst_range_raw)) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

stab_data_x %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O") %>%
  ggplot(aes(x = SB_var_gmax_s,
             ymin = hyst_min_raw,
             ymax = hyst_max_raw)) +
  geom_ribbon(alpha = 0.5) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )
```

### log
```{r, eval = FALSE, echo = FALSE}
stab_data_x %>%
  filter(Species == "O") %>%
  ggplot(aes(x = SB_var_gmax_s, y = hyst_range_log)) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

stab_data_x %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O") %>%
  ggplot(aes(x = SB_var_gmax_s,
             ymin = hyst_min_log,
             ymax = hyst_max_log)) +
  geom_ribbon(alpha = 0.5) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )
```

## 2x CB, 6xSBPB diversity

@@

@@

@@

### raw
```{r}
all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range_raw, col=var_treat, shape = as_factor(sim_length))) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

@@

### log
```{r}
all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range_log, col=var_treat, shape = as_factor(sim_length))) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

@@

# Zoom in on SS

@@

# Negative abundance investigation

@@

# Understand about relative and absolute variation in traits

>>>>

@@

sp <- new_strain_parameter(
  n_CB = num_CB_strains,
  n_PB = num_SB_strains,
  n_SB = num_PB_strains,
  values_initial_state = "bush_ssfig3"
)

@@

@@

```{r}
## Here we get some rows of var_expt that correspond with particular diversity levels

var_expt_levels <- var_expt[, 1:6]

@@

max_only_SBPB_diversity <- which(
  max(rowSums(abs(var_expt_levels[, 3:6]))) == rowSums(abs(var_expt_levels[, 3:6])) &
  rowSums(abs(var_expt_levels[, 1:2])) == 0
)
#var_expt_levels[20,]

medium_diverity_varexp_row <- 311

@@

```{r eval = eval_dynamics_flag}
parameter$sim_duration <- 80000
```

```{r eval = eval_dynamics_flag}
parameter$log10a_series <- c(-1, -7, -7)
parameter$strain_parameter <- var_expt$pars[[no_diversity]]
parameter$strain_parameter$initial_state <- new_initial_state(
  num_CB_strains,
  num_PB_strains,
  num_SB_strains,
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/num_CB_strains
sim_res_novar1 <- run_simulation(parameter)
saveRDS(sim_res_novar1, here("experiments/experiment 1/data/sim_res_novar1.RDS"))
```

@@

```{r eval = eval_dynamics_flag}
parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
parameter$strain_parameter$initial_state <- sim_res_novar1$strain_parameter$initial_state
sim_res_highvar1 <- run_simulation(parameter)
saveRDS(sim_res_highvar1, here("experiments/experiment 1/data/sim_res_highvar1.RDS"))
```

@@

```{r eval = eval_dynamics_flag}
parameter$log10a_series <- c(-5, -3, -1, -1)
parameter$strain_parameter <- var_expt$pars[[no_diversity]]
parameter$strain_parameter$initial_state <- new_initial_state(
  num_CB_strains,
  num_PB_strains,
  num_SB_strains,
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
sim_res_novar2 <- run_simulation(parameter)
saveRDS(sim_res_novar2, here("experiments/experiment 1/data/sim_res_novar2.RDS"))
```

@@

```{r eval = eval_dynamics_flag}
parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
parameter$strain_parameter$initial_state <- sim_res_novar2$strain_parameter$initial_state
sim_res_highvar2 <- run_simulation(parameter)
saveRDS(sim_res_highvar2, here("experiments/experiment 1/data/sim_res_highvar2.RDS"))
```

@@

```{r eval = eval_dynamics_flag}
parameter$log10a_series <- c(-1, -8, -1)
parameter$strain_parameter <- var_expt$pars[[no_diversity]]
parameter$strain_parameter$initial_state <- new_initial_state(
  num_CB_strains,
  num_PB_strains,
  num_SB_strains,
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
sim_res_novar3 <- run_simulation(parameter)
saveRDS(sim_res_novar3, here("experiments/experiment 1/data/sim_res_novar3.RDS"))
```

@@

```{r eval = eval_dynamics_flag}
parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
parameter$strain_parameter$initial_state <- sim_res_novar3$strain_parameter$initial_state
sim_res_highvar3 <- run_simulation(parameter)
saveRDS(sim_res_highvar3, here("experiments/experiment 1/data/sim_res_highvar3.RDS"))
```

@@

### Ecosystem-environment relationship

@@

```{r}
minimum_abundances <- rep(0, 3)
names(minimum_abundances) <- c("CB", "PB", "SB")

grid_num_a <- 1000 #usually 1000 ## number of a_0 values
#grid_num_a <- 10 ## FOR TEST
a_Os <- 10^seq(-7, -0.5, length=grid_num_a) ## sequence of a_0 values
grid_num_N <- 2 ## number of N values
initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
initial_PBs <- 1e8 ## not varied
initial_SBs <- 1e8 ## not varied
# next line creates all possible combinations
ss_expt <- expand.grid(N_CB = initial_CBs,
                      N_PB = initial_PBs,
                      N_SB = initial_SBs,
                      a_O = a_Os)

parameter <- new_ss_by_a_N_parameter(
  dynamic_model = parameter$dynamic_model,
  event_definition = parameter$event_definition,
  event_interval = 1000000,
  noise_sigma = parameter$noise_sigma,
  minimum_abundances = minimum_abundances,
  sim_duration = 1000000,
  sim_sample_interval = 1000000,
  log10a_series = parameter$log10a_series,
  solver_method = parameter$solver_method,
  ss_expt = ss_expt
)
rm(minimum_abundances, grid_num_a, a_Os, grid_num_N, initial_CBs, initial_PBs, initial_SBs, ss_expt)

saveRDS(parameter, here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS"))
saveRDS(var_expt_small, here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial.RDS"))
```

### for testing

```{r eval = FALSE}
var_expt_small <- var_expt[c(no_diversity, medium_diverity_varexp_row),]
saveRDS(parameter, here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS"))
saveRDS(var_expt_small, here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial_small.RDS"))
run_ss_var_experiment(
  parameter = readRDS(here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS")), 
  var_expt = readRDS(here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial_small.RDS"))) %>%
saveRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_small.RDS"))
```

@@

## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_small.RDS")) %>%
  mutate(sim_length = 1000000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial_small.RDS"))
```

```{r eval = FALSE}
## compare version 1 results to the current.
v1_ss_data <- readRDS(here("experiments/experiment 1/data/version1_ss_data_1e6_x2x6_factorial.RDS"))
v1_stab_data <- readRDS(here("experiments/experiment 1/data/version1_stab_data_1e6_x2x6_factorial.RDS"))

small_ss_data <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_small.RDS"))
small_stab_data <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial_small.RDS"))

xxxxx <- small_stab_data %>%
  select(-data, -pars, -ss_by_a_N_result, -ss_res, -sim_length) %>%
  filter(Species == "O")
v1_stab_data %>%
  filter(CB_var_gmax_s == 0, CB_var_h_s == 0,
         SB_var_gmax_s == 0, SB_var_h_s == 0,
         PB_var_gmax_s == 0, PB_var_h_s == 0) %>%
  filter(Species == "O")
v1_stab_data %>%
  slice(9620) %>%
  filter(Species == "O")
```

@@

medium_diverity_varexp_row <- 311

@@

### Display results

@@

### Raw
```{r}
all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range_raw, col=var_treat, shape = as_factor(sim_length))) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

@@

### Log transformed

```{r}
all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range_log, col=var_treat, shape = as_factor(sim_length))) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

@@

## Zoom in on SS

@@

## Negative abundance investigation

@@

## Understand about relative and absolute variation in traits
